%-------------------------
% Fullstack Developer Resume in Latex
% Author : Dan Li
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{mathtools} 
\usepackage{amsmath} 
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\newcommand{\projectSubheading}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} \(|\) \textit{#2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\projectItem}[1]{
  \item\small{
    #1 \vspace{-2pt}
  }
}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[left=0em]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large{Dan Li}} & Email : \href{mailto:d22li@uwaterloo.ca}{\underline{d22li@uwaterloo.ca}}\\
  \href{https://github.com/danmxli}{\underline{https://github.com/danmxli}} & Mobile : +1-647-675-6975 \\
\end{tabular*}


%--------SKILLS------------
\section{Skills}

     \small\textbf{Languages}{: Python, Typescript, Javascript, C/C++, SQL, Java, Bash}
     \newline
     \small\textbf{Tools, Databases, Platforms}{: Git, MongoDB, PostgreSQL, Docker, AWS}
     \newline
     \small\textbf{Libraries and Frameworks}{: React.js, NumPy, Flask, Django, FastAPI, PyTorch, Next.js, Express.js}


%-----------WORK EXPERIENCE-----------------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Onlia Insurance}{Toronto, ON}
      {Automation Developer}{May 2023 - Aug 2023}
      \resumeItemListStart
        \resumeItem{Regression Testing}
          {Led the development of a regression testing tool using Selenium with Java, and TestNG.}
        \resumeItem{Test Optimization}
          {Leveraged Java interfaces to define default implementations for Page Object Models, resulting in a 38\% increase in regression test coverage.}
        \resumeItem{Reporting}
          {Refined Selenium WebDriver exception handling capabilities, resulting in a 15\% reduction in the occurrence of incorrect pass-fail reporting instances.}
        \resumeItem{Business-logic Testing}
          {Configured and executed a back-end project to perform integration tests for policy binding and account activation services.}
        \resumeItem{Data Retrieval}
          {Developed a SOAP web service to retrieve data for policy binding and activation; utilized the JDBC API with PostgreSQL for program-to-database communication.}
        \resumeItem{File Writing}
          {Configured Excel writing capabilities with Apache POI to generate spreadsheets of activated accounts for automated testing usage, resulting in a 23\% increase in QA resources.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart

  \projectSubheading{\href{https://github.com/ericqiu04/project}{\underline{Instagram Marketing and Content Growth Service}}}{Typescript, Python, PostgreSQL}
      \resumeItemListStart
        \projectItem{Worked in a 2-man team to build a SaaS for content creators to boost their digital presence; architected an Instagram hashtag recommendation API with Django REST framework.}
        \projectItem{Implemented RLS and Postgres policies to restrict CRUD operations per user and prevent unauthorized row access.}
        \projectItem{Leveraged the ResNet50 neural network with PyTorch for image classification to refine Instagram hashtag generation per post.}
      \resumeItemListEnd

  \projectSubheading{\href{https://github.com/danmxli/Conduify}{\underline{Agent-integrated Interview Preparation Tool}}}{Typescript, Python, MongoDB}
      \resumeItemListStart
        \projectItem{Developed an agent capable of interview simulation and resume evaluation with Cohere and OpenAI's LLMs.}
        \projectItem{Utilized Beautiful Soup to scrape data from the applicant's company of interest; leveraged PDF parsing modules in Python to refine hierarchical information extraction from applicant resume.}
        \projectItem{Used MongoDB vector database to store company and resume data as query and document embeddings; relevancy of resume contexts to company data were determined by the dot product of the respective vectors.}
        \projectItem{Reduced hallucinations by grounding the model on contexts, improving LLM generation to build human trust.}
      \resumeItemListEnd
    \projectSubheading{\href{https://github.com/danmxli/seePickle}{\underline{Productivity Visualization Tool - Hackfest November 2023}}}{Typescript, Python, MongoDB}
      \resumeItemListStart
        \projectItem{Architected the UI, REST API, and schema models to build and deploy a cloud-based planning tool with Cohere's LLMs. Won the "Best Use of MongoDB Atlas" and "Best Use of Auth0" awards.}
        \projectItem{Designed MongoDB aggregation pipelines to optimize CRUD operations, achieving over 8.5x faster performance than manual iteration into document data.}
        \projectItem{Leveraged the React Flow library to display sequential data as an interactive node-based flowchart.}
        \projectItem{Developed authentication-required routes with a "redirect" functionality to safeguard user-sensitive data.}
      \resumeItemListEnd
    \projectSubheading{\href{https://github.com/danmxli/ChicSplain}{\underline{YouTube Content Analysis Chatbot - Hack The Valley 8}}}{Python, MongoDB}
      \resumeItemListStart
        \projectItem{Collaborated in a team of 4 to build a Chatbot as a Service with Cohere's LLMs; led development of the REST API to provide the business-logic layer and user management. Won the "Best Use of MongoDB Atlas" award.}
        \projectItem{Integrated the YouTube Data API with string searching algorithms to optimize video context summarization.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Waterloo}{Waterloo, ON}
      {Candidate for Computer Engineering Honours, Co-operative Program}{Sept 2022 -- Apr 2028}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
